### 2019-10-15 tesis_hiram/Chapter3/chapter3.tex
algo

\section{Event Selection}
In order to detect signal events and reject background, the following selections are applied. 
\begin{itemize}
	\item The events must contain two muons with the same sign.
	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
	\item One or more b-tagged jets with  $|\eta|$ < 2.4
\end{itemize}
%Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
The number of events that passed the event selection are shown in table \ref{tth-table} which corresponds to  a integrated luminosity of 35.9 fb$^{-1}$ \cite{th1}.
The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes. For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling  scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10. 
This event yields  will be used to estimate the signal sensitivity.The yields include statitical uncertanties due to the simulated samples and systematic uncertanties are described below. 
\begin{table}[ht!]
	\centering
\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$. The uncertainties of yields include statistical and systematic}
	\begin{tabular}{cc}
	\hline
		Process  & Number of events  \\
		\hline
		$t\bar{t}W$  &  68 $\pm$ 10 \\
		$t\bar{t}Z$  & 25.9 $\pm$ 3.9\\
		$WZ$ & 15.1$\pm$7.7\\
		Rares & 20.9 $\pm$   4.9\\
		Fakes  & 80.9 $\pm$9.4\\
	   $t\bar{t}H$  &  24.2 $\pm$ 2.1 \\
		\hline
		$tH$ (SM) & 2.14 $\pm$ 0.13\\
		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
	\end{tabular}	
\label{tth-table}
\end{table}

>>>>

\section{Event Selection}
In order to detect signal events and reject background, the following selections are applied. 
\begin{itemize}
	\item The events must contain two muons with the same sign.
	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
	\item One or more b-tagged jets with  $|\eta|$ < 2.4
\end{itemize}
%Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
The number of events that passed the event selection are shown in table \ref{tth-table} which corresponds to  a integrated luminosity of 35.9 fb$^{-1}$ \cite{th1}.
The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes. For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling  scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10. 
This event yields  will be used to estimate the signal sensitivity. The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertanties are described below. 
\begin{table}[ht!]
	\centering
\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$. The uncertainties of yields include statistical and systematic}
	\begin{tabular}{cc}
	\hline
		Process  & Number of events  \\
		\hline
		$t\bar{t}W$  &  68 $\pm$ 10 \\
		$t\bar{t}Z$  & 25.9 $\pm$ 3.9\\
		$WZ$ & 15.1$\pm$7.7\\
		Rares & 20.9 $\pm$   4.9\\
		Fakes  & 80.9 $\pm$9.4\\
	   $t\bar{t}H$  &  24.2 $\pm$ 2.1 \\
		\hline
		$tH$ (SM) & 2.14 $\pm$ 0.13\\
		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
	\end{tabular}	
\label{tth-table}
\end{table}

### 2019-10-15 tesis_hiram/Chapter4/chapter4.tex
algo

	\begin{table}[ht!]
		\centering
		\caption{Postfit  yields for the fit to the Asimov data corresponding to 35.9 /fb. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process  & SM    & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$  &  68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$  & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ &  15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares &  20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes  &  80.9$\pm$9.0&  80.9$\pm$8.9 \\
			$t\bar{t}H$  &   24.2$\pm$2.0 &  24.2$\pm$2.0 \\
			\hline
			$tH$&  2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}

@@

@@

	\pagebreak
	\section{Limit calculation}
	Due to the large background, the signal strength for the Asimov data with 35.9 $fb^{-1}$ is consistent with zero.
	Therefore, we estimate an upper limit on the signal strength at 95$\%$  confidence level.\\

@@

	\begin{figure}[ht!]
		\centering
		\includegraphics[scale=0.5]{Chapter4/chi_squared.png}
		\caption{Illustration of the $\chi^2$  distribution with number of degrees of freedom of 7 used for the limit estimation}
		\label{chi}
	\end{figure}

	\begin{figure}[!htbp]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
		\end{minipage}
		\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
		\label{scanl}
	\end{figure}

	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
	\section{Extrapolation for higher luminosities}
	In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9fb $^{-1}$ is not significant. The LHC has already collected data for integrated luminosity of 150fb $^{-1}$ for run 2 finished in 2018. Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb . Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities. 
	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly. For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same.
	\\

	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities. As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1. But even with the increase of number of events, the ratio of signal and data is still very small.  In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases. This is caused by the increased events available for the fit. 
	\pagebreak

@@

	\begin{figure}[!htbp]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/simple-150-kt-1.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/simple-300-kt-1.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/simple-3000-kt-1.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/Likelihood.png}
		\end{minipage}
		\caption{Fit and likelihood scan for 150fb $^{-1}$, 300fb $^{-1}$ and 3000fb $^{-1}$ in $k_t$=-1 model.}
		\label{hm1}
	\end{figure}
	The same method is used for the model $k_t$=-1 in the figure \ref{hm1}. In this case, the number of events for the signal is more appreciable in comparison with the SM model, same as the 35.9fb $^{-1}$ case. However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case. For the 3000 fb $^{-1}$ case, the curve closes in $\mu \approx $2. 
	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}

	\begin{table}[ht!]
		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			Luminosity (fb $^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
			\hline
			35.9 & 1.0 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
			\hline
			150& 1.0 $\pm$  6.7& 11  &  1.0 $\pm$  0.4 &1.8\\
			\hline
			300&1.0 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
			\hline
			3000&1.0 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
			\hline
		\end{tabular}
		\label{upper}
	\end{table}

@@

	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$. 
	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data. This is caused by the fact that the uncertainty of $k_t$=-1 model has a lower uncertainty than the SM model and the number of events for the $tH$ signal is greater. For 3000 fb$^{-1}$ the uncertainty on mu is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.

>>>>

@@

	\begin{table}[ht!]
		\centering
		\caption{Postfit  yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process  & SM    & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$  &  68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$  & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ &  15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares &  20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes  &  80.9$\pm$9.0&  80.9$\pm$8.9 \\
			$t\bar{t}H$  &   24.2$\pm$2.0 &  24.2$\pm$2.0 \\
			\hline
			$tH$&  2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}

@@

	\pagebreak
	\section{Limit calculation}
	Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
	Therefore, we estimate an upper limit on the signal strength at 95$\%$  confidence level.\\

@@

	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
	\section{Extrapolation for higher luminosities}
	In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9 fb$^{-1}$ is not significant. The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 finished in 2018. Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb . Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities. 
	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly. For this analysis we assume the systematic uncertainties assigned to the background are the same.
	\\

	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities. As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1. But even with the increase of number of events, the statistical uncertainty of the data is too large with respect to the expected signal.  In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases. This is caused by the increased events available for the fit. \\

	The same method is used for the model $k_t$=-1 in the figure \ref{hm1}. In this case, the number of events for the signal is more appreciable in comparison with the SM model. However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case. 
	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}\\

	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 170$\%$ in the 3000 fb$^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results to reduce the uncertainty on $\mu$ for a possible observation of the signal. 
	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small. This is caused by the fact that the number of events for the $tH$ signal is greater. For 3000 fb$^{-1}$ the uncertainty on $\mu$ is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.

	\begin{table}[ht!]
		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
		\begin{tabular}{|c|c|c|c|c|}
			\hline
			Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
			\hline
			35.9 & 1.0 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
			\hline
			150& 1.0 $\pm$  6.7& 11  &  1.0 $\pm$  0.4 &1.8\\
			\hline
			300&1.0 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
			\hline
			3000&1.0 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
			\hline
		\end{tabular}
		\label{upper}
	\end{table}

	\pagebreak

		\begin{figure}[ht!]
		\centering
		\includegraphics[scale=0.65]{Chapter4/chi_squared.png}
		\caption{Illustration of the $\chi^2$  distribution with number of degrees of freedom of 7 used for the limit estimation}
		\label{chi}
	\end{figure}

	\begin{figure}[!htbp]
		\centering
		\begin{minipage}[b]{0.55\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.55\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
		\end{minipage}
		\caption{Likelihood scan for SM (up) and $k_t$=-1 (Down).}
		\label{scanl}
	\end{figure}
	\pagebreak

@@

	\begin{figure}[!htbp]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/simple-150-kt-1.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/simple-300-kt-1.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/simple-3000-kt-1.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/Likelihood.png}
		\end{minipage}
		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in $k_t$=-1 model.}
		\label{hm1}
	\end{figure}

@@

### 2019-10-15 tesis_hiram/Chapter5/chapter5.tex
algo

\chapter{Conclusion and outlook}

\chapter{Conclusion and outlook}
In this work, we explored the $tH$ processes and its different decay rates, including the Higgs mechanism that generate the bosons involved in theses processes. 
The $tH$ process is one of the processes that comes from the proton-proton collisions inside the accelerators. But due to the maintenance schedule of the LHC, many researchers uses Monte Carlo simulation and real data or even only MC for analyze the results and create predictions. In our case, by using MC simulations with an Asimov data, it was obtained a fit for the Asimov data with a model of signal and background events with systematic uncertainties according to the decay of processes to a pair of same sign muons $\mu$. \\

In the results for SM case, we got for the actual luminosities that the signal strength for the signal $tH$ is very low and that generates a signal-data ratio very small in comparison to the backgrounds, generating great uncertainties. For that, it was used extrapolations of the model by increasing the luminosity according to the LHC schedule, and discovered that by increasing the number of events, the signal uncertainties was decreasing, and improving the fit. In the likelihood scans in higher luminosities, the curves were closing, indicating that the model and the data incompatibility was decreasing in lower values of $\mu$. 
\\

However, for the $k_t$=-1, the uncertainty for the model after the fit was less than the SM case, so by increasing the luminosity the compatibility of model and the data was decreasing for higher luminosities, given that the $\mu$ in the likelihood scan w

All the research made in the CMS at CERN has let us discover the nature of the matter and try to answer questions about the origin of the universe, including the origin of the mass of the things. \\

>>>>

\chapter{Conclusion and outlook}
In this work, we explored the $tH$ processes and its different decay rates. 
The $tH$ process is one of the processes that comes from the proton-proton collisions in the LHC. This process has not been observed experimentally. Recently CMS published a search for $tH$ process using 35.9 fb$^{-1}$ from Run 2 in 2018. \\

MC simulation and real data or even only MC can be used to study sensitivity different signal processes. In this work we used the information from CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons. \\
In the SM case, the signal strength for the signal $tH$ is very low in comparison to
the backgrounds, resulting in large uncertainties.
For the inverted coupling scenario ($k_t$=-1), the uncertainty for the model after the fit was better than the
SM case, this is due to the larger expected number of signal events. However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels.
\\

We also studied the sensitivity for larger integrated luminosities expected in future runs of the LHC. We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed. In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb${-1}$.\\
